Mitigating object prior-bias from sparse-projection tomographic reconstructions

### 2022-02-16 paper/response_2022.tex

\section{Comments from AE}

\textcolor{blue}{\textit{While the reviewers have acknowledged
    improvements compared to the earlier manuscript, they have raised
    some important concerns about the manuscript in its current
    form. While addressing each of the reviewer specific comments,
    please pay specific attention to the following:}}

  \begin{itemize}
  \item \textcolor{blue}{\textit{Characterization of deep learning
        methods and its relation to the presented work}}

    We have now included a discussion of deep-learning (DL) methods in
    `Related Work', Section 2, of our paper, and have cited a few
    notable references pertaining to training neural networks to
    directly predict full-view sinogram and reconstruct the test
    object from its limited-view measurements. We also discuss how our
    work is complementary to learning-based teachniques and can fit
    alongside a recent, state of the art, deep learning framework, as
    seen in Fig.~2 of the paper. Hence, the ability of DL to uncover
    new features is not being disputed. Instead, our focus is on a
    novel discrete method.

@@

\vspace{0.5cm}\textcolor{blue}{\textbf{[R2-3]:} \textit{In several parts of the
    paper, the authors claim that existing object-prior based methods
    have problems, e.g.: "A common problem with these techniques is
    the strong influence of object-priors in the reconstruction of new
    regions in the test". At the moment, this hard claim is not
    supported in the paper by references or (even better) comparison
    results. It would be good to show, on one (or more) of the
    datasets used, that this is indeed the case, and that the proposed
    methods solves this problem.}}

\textbf{Response:} We have now included a reference (Pg.2, Line 3
under Sec.1-A) to a PhD thesis. This thesis discusses the problem of object-priors biasing the reconstruction of new test regions.
A sample result (Figures 1-3) from the thesis is shown here. It
illustrates how a direct application of object-prior can adversely
affect the reconstruction of new regions in the test.

\vspace{0.5cm}\textcolor{blue}{\textbf{[R2-4]:} \textit{The discussion of deep learning methods in Section 7B is not very strong in my opinion. There are many existing techniques that have shown quite convincing results for reconstructing CT images with a low number of projections, even without taking into account any static parts across time. These methods rely on learning image-based correlations instead of the "given intensities of a voxel at various time instants in a longitudinal setting and partial measurements of the voxel at the current time, what will be the intensity of the same voxel at the current time instant?" given by the authors. These image-based methods often don't need 'hundreds of labeled data', sometimes being able to accurately learn from just one time step. In the paper, these methods should be discussed, and proper references should be included.}}\\

\textbf{Response}: We acknowledge that there has been significant work
pertaining to training neural networks to directly predict full-view
sinogram and reconstruction of the test object from its limited-view
measurements. We have now included a discussion of deep-learning
methods in `Related Work', Section 2, of our paper, and have now cited
a few notable references. We also discuss how our work is
complementary to learning-based teachniques and can fit alongside a
deep learning framework, as seen in Fig.~2 of the revised paper. That
said, the focus of our work is on a new discrete algorithm that builds
structural maps that can and does point to new features.

### 2022-02-17 paper/response_2022.tex

  \begin{table}[h!]
    \centering
    \begin{tabular}{|l|l|l|l|}
      \hline
      & \textbf{\begin{tabular}[c]{@{}l@{}}Ground\\ truth\end{tabular}} & \textbf{FDK} & \textbf{TV} \\ \hline
      \textbf{Minimum} & 0.00 & -0.19 & 0.00 \\ \hline
      \textbf{Maximum} & 1.00 & 0.24 & 0.24 \\ \hline
    \end{tabular}
    \caption{ \label{Tab:ranges} Example. Minimum and maximum
      intensity values of groundtruth and reconstructed volumes of
      potato data reconstructed from 18 views.}
  \end{table}

  \item

    [\hypertarget{ssim}{Meta comment:}  This section is also in response to \hyperlink{ssim-R1}{R1} (\ldots \emph{SSIM
      have their own definitions}\ldots]

    [Standard vs custom:] We have used the commonly used SSIM metric,
    for which, we have now provided reference to the original paper
    where the metric has been defined. As is well known, SSIM comprises
    of three factors: Luminance, Contrast and Structure. These factors
    (now termed `coefficients', earlier `weights') for these
    three terms are adjustable to suit the application at hand.  Since
    SSIM inherently offers a flexibility to set coefficients based on
    what we want to evaluate, we believe that having a set of
    coefficients that focus on measuring structural preservation is
    better suited for our goal.

@@

\textbf{Comments:} The paper presents an image reconstruction method for recovering samples from limited projections provided that the high-quality CT-scans of the same sample exist. This approach could be useful to longitudinal studies in which the patient's previous CT scans are available and the purpose is to reduce the dose. So this is good!\\

The structure of the paper is good and the authors did a good job in presenting both the theory and the validation with experimental data, demonstrating the potential. of the nice things about the paper is that they use PCA to get the orthonormal basis to represent the image and this both serves as a regularizer as well as a nice way to quantify new features in data.
\\

\vspace{0.5cm}\textcolor{blue}{\textbf{[R3-1]:} \textit{One challenge of the method that I can see is that these datasets needs to be aligned but there is not much discussion on this procedure or how this can be performed in a realistic setting. Are the variation from a past to present scans looking similar? In addition to the variations in scans taken at different times, in the low-quality scan, the features are less pronounced so the registration might pose a challenge even if the sample looks similar. So, it would be good to see the artifacts due to an intentionally less-aligned images and a discussion about the limitations would be nice.
}}\\

\textbf{Response}: Yes, registration between the unknown test and templates is important for our method. Registration is also a common problem in many other fields such as MRI/CT/PET data.  There is a lot of research on linear and non-linear methods to optimise this. The focus in our paper is not on registration but on building accurate maps that delineate regions of structural changes in already pre-registered data (registered using state-of-the-art methods).  Hence, in this work, we do not intend to predict what difficulties registration might present but rather that show that it is possible to blend prior and new views.
%We note that in practice, a pilot reconstruction of the test must be registered with similarly imaged, pilot reconstructed templates. This registration is challenging due to the presence of sub-sampling artefacts.
We consider the problem of registration as a separate one and intend the practitioners to use any state-of-the-art registration algorithm, such as~\cite{robert2021},\cite{registrationThesis}, before applying the proposed method in our paper. 
\\
